% !TEX root = ../proposal.tex

\paragraph{\WPManagement: \WPManagementTitle \\}

{\noindent\wptablefont

\wptableheaderA{\WPManagementTitle}{\WPManagement}{M1}{MGT}{\COORD}
\wptableheaderB{\WPManagementVW}{\WPManagementETHZ}{\WPManagementIBM}{\WPManagementCLUJ}{\WPManagementPRAGUE}


\headerBox{Objectives}{}

The \Project{} project management structure is characterized by the following formal roles: Project Coordinator and Steering Committee; Work package leaders. In terms of formal process, the work package leaders will be responsible for the planning, scientific management and progress of their work package and will have to report the progress to the Project coordination team. The Steering Committee -- formed by representative from each partner -- serves as the main forum for decisions and the responsible instance to resolve disputes.

The main objectives within this work package are as follows:
\begin{denseItemize}
\item Negotiation and signing of the consortium agreement (to be signed before the project start)
\item Monitoring of the project, ensuring the fulfillment of the consortium's contractual obligations
\item Ensuring the quality of the work and the deliverables being produced
\item Ensuring smooth progress and execution of the project by providing administrative, financial and technical management
\item Provision of the necessary liaisons between the consortium, the EU and other consortia
\end{denseItemize}


\begin{tasks}{\WPManagementNo}
\item {\bf Project management}
\label{task:wpmanagement:management}
\taskpartners{\COORD}{ all other partners}

Project management is addressed by the first task of this work package spanning the entire duration of the project. Project management aims at:
\begin{denseItemize}
\item coordinating the joint efforts of the consortium during the execution of the project,
\item ensuring the smooth progress of the work plan and the fulfillment of the consortium's contractual obligations,
\item providing the necessary liaisons between the consortium, the EU as well as other consortia and
\item ensuring the quality of the work and the deliverables being produced.
\end{denseItemize}

The responsibility for the key management-related activities will be carried by the \Project{} Steering Committee, see Section~\ref{sec:mngt:ga} on page~\pageref{sec:mngt:ga} for details.


\item {\bf Project status monitoring}
\label{task:wpmanagement:monitoring}
\taskpartners{\COORD}{ all other partners}

An important aspect of successful project management is the knowledge about the status of the project at all time. To timely react to upcoming problems or delays, yearly progress reports are in general not sufficient. Thus, we will monitor the progress of the partners continuously based on comparably informal status reports provided to the Project Coordination team.  The Project Coordinator will monitor the status of the project from the
management and from the research point of view.
%The Administrative Project Manager will summarize the current project status from the administrative point of view.
This will allow us to timely react to problems, measure the progress in the \Project{} project and thus provide the prerequisites for a successful execution of the overall project.

The Project Coordinator will be \Coordinator{} from \COORD{}. Note that large parts of the \Project consortium already worked together successfully within other EU projects.
\end{tasks}


\begin{deliverables}{\WPManagementNo}

\item {\bf  Periodic status report year 1} \putright{\bf M12}
	\delresponsible{\VW}

The deliverable provides a technical report on the overall status of the project every year. The first report will describe the status of the specifications, as well as the advancements reached in each WP. 

\item {\bf  Periodic status report year 2} \putright{\bf M24}
	\delresponsible{\VW}

The deliverable provides a technical report on the overall status of the project every year. The second report will describe the status of the the first iteration of research and development as well as the advancements reached in each WP.

\item {\bf  Periodic status report year 3} \putright{\bf M36}
	\delresponsible{\VW}

The deliverable provides a technical report on the overall status of the project every year. The third report will describe the status of the the second iteration of specifications and integration and evaluation, as well as the advancements reached in each WP.

\item {\bf  Periodic status report year 4} \putright{\bf M48}
	\delresponsible{\VW}

The deliverable provides a technical report on the overall status of the project every year. The fourth report will describe the status of the the second iteration of specifications and integration and evaluation, as well as the advancements reached in each WP.

\end{deliverables}


}






